Step 13: Marginal Effects Analysis with Multiple Imputation

### 2025-09-08 reanalysis-13-marginal_effects.qmd
more resilient mfx

```{r calculate-all}
# Now run for all imputations
all_mfx_results <- list()

# Initialize storage for each subgroup
for (sg_name in names(subgroups)) {
  all_mfx_results[[sg_name]] <- list()
}

@@

# Process each imputation
for (i in 1:n_imputations) {
  if (i %% 10 == 1) {
    cat(paste0("Processing imputations ", i, "-", min(i+9, n_imputations), "...\n"))
  }

@@

@@

# Save intermediate results
saveRDS(all_mfx_results, file.path(marginal_effects_dir, "all_mfx_results.rds"))
log_message("Saved all marginal effects results")
```

@@

```{r pool-mfx}
# Pool the marginal effects across imputations
pooled_mfx <- list()

@@

# Save pooled results
saveRDS(pooled_mfx, file.path(marginal_effects_dir, "pooled_mfx_results.rds"))
log_message("Saved pooled marginal effects")
```

@@

# Display table
kable(summary_df,
      caption = "Pooled Average Marginal Effects of Lapsing by Subgroup",
      align = c("l", "r", "r", "c", "r", "r", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  add_header_above(c(" " = 1, 
                     "Marginal Effect" = 2,
                     "Statistical Inference" = 2,
                     "Sample" = 2))

>>>>

```{r calculate-all}
# Check if we have cached results to resume from
cached_results_file <- file.path(marginal_effects_dir, "all_mfx_results.rds")
if (file.exists(cached_results_file)) {
  cat("Loading cached marginal effects results...\n")
  all_mfx_results <- readRDS(cached_results_file)

  # Check which imputations are complete
  completed_imps <- c()
  for (i in 1:n_imputations) {
    if (length(all_mfx_results[[1]]) >= i && 
        !is.null(all_mfx_results[[1]][[i]])) {
      completed_imps <- c(completed_imps, i)
    }
  }

  if (length(completed_imps) > 0) {
    cat(paste0("Found ", length(completed_imps), " completed imputations\n"))
    cat(paste0("Will resume from imputation ", max(completed_imps) + 1, "\n\n"))
  }
} else {
  # Initialize new storage
  all_mfx_results <- list()

  # Initialize storage for each subgroup
  for (sg_name in names(subgroups)) {
    all_mfx_results[[sg_name]] <- list()
  }
  completed_imps <- c()
}

@@

# Process each imputation
for (i in 1:n_imputations) {
  # Skip if already completed
  if (i %in% completed_imps) {
    next
  }

  if (i %% 10 == 1) {
    cat(paste0("Processing imputations ", i, "-", min(i+9, n_imputations), "...\n"))
  }

@@

  # Save intermediate results every 5 imputations
  if (i %% 5 == 0) {
    saveRDS(all_mfx_results, cached_results_file)
    cat(paste0("  [Checkpoint] Saved results through imputation ", i, "\n"))
  }

@@

# Save final results
saveRDS(all_mfx_results, cached_results_file)
log_message("Saved all marginal effects results")
```

@@

```{r pool-mfx}
# Check if we have pooled results cached
pooled_results_file <- file.path(marginal_effects_dir, "pooled_mfx_results.rds")

if (file.exists(pooled_results_file)) {
  cat("Loading cached pooled results...\n")
  pooled_mfx <- readRDS(pooled_results_file)
} else {
  # Pool the marginal effects across imputations
  pooled_mfx <- list()
}

@@

# Save pooled results if not already cached
if (!file.exists(pooled_results_file)) {
  saveRDS(pooled_mfx, pooled_results_file)
  log_message("Saved pooled marginal effects")
} else {
  log_message("Using cached pooled marginal effects")
}
```

@@

# Display table - simplified to avoid kable errors
if (nrow(summary_df) > 0) {
  # Use basic kable without complex styling that can fail with long data
  print(kable(summary_df,
        caption = "Pooled Average Marginal Effects of Lapsing by Subgroup",
        align = c("l", "r", "r", "c", "r", "r", "r"),
        digits = 4))
} else {
  cat("No results to display in summary table\n")
}
